Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-15 ms.tex
start switching to vector notation for intensities in MCMC discussion, move second EBV residual figure

\begin{equation}
\label{eqn:post}
P(\tilde{I}_{545}, T_2|\{I\}) \propto \mathcal{L}(\{I\}|\tilde{I}_{545}, T_2)P(T_2)P(\tilde{I}_{545})
\end{equation}

@@

Here \{$I$\} denotes the set of observed intensities quoted under
the `IRAS convention': $I_{217}$, $I_{353}$, ... The likelihood function is 
given by:

\begin{equation} \label{equ:like}
\mathcal{L}(\{I\}|\tilde{I}_{545}, T_2) = \displaystyle\prod\limits_{i}\mathcal{N}(\tilde{I}_{\nu_{i}}|I_{\nu_{i}}, \sigma_{\nu_i})
\end{equation}

@@

Where the product runs over $\nu_i$ in $\{217,\ 353,\ 545,\ 857,\ 3000\}$ GHz
and $\tilde{I}_{\nu_i}$ is a function of $\tilde{I}_{545}$ and $T_2$ as 
specified by Equation \ref{eqn:inten}. For each pixel, the errors on each 
intensity measurement $\sigma_{\nu_i}$ are given by:

>>>>

\begin{equation}
\label{eqn:post}
P(\tilde{I}_{545}, T_2|\vec{I}~) \propto \mathcal{L}(\vec{I}~|\tilde{I}_{545}, T_2)P(T_2)P(\tilde{I}_{545})
\end{equation}

@@

Here $\vec{I}$ denotes the vector of observed intensities quoted under
the `IRAS convention': $\vec{I}$ = ($I_{217}$, $I_{353}$, ..., $I_{3000}$). The
likelihood function is given by:

\begin{equation} \label{equ:like}
\mathcal{L}(\vec{I}~|\tilde{I}_{545}, T_2) = \displaystyle\prod\limits_{i}\mathcal{N}(\tilde{I}_{\nu_{i}}|I_{\nu_{i}}, \sigma_{\nu_i})
\end{equation}

@@

Where the product runs over $\nu_i$$\in$$\{217,\ 353,\ 545,\ 857,\ 3000\}$ GHz
and $\tilde{I}_{\nu_i}$ is a function of $\tilde{I}_{545}$ and $T_2$ as 
specified by Equation \ref{eqn:inten}. For each pixel, the uncertainty on each 
intensity measurement $\sigma_{\nu_i}$ is given by:
